Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-07-15 ms_figure_2_overview-heatmaps.Rmd
Move IP-MS PCA plots to SuppFig 2

```{r load-packages, class.source="fold-show"}
suppressPackageStartupMessages({
    library(SingleCellExperiment)
    library(ggplot2)
    library(cowplot)
    library(dplyr)
    library(forcats)
    library(jsonlite)
    library(ComplexHeatmap)
    library(colorspace)
    library(circlize)
    library(scattermore)
    library(tidyr)
})

@@

@@

cowplot::plot_grid(
    gg_enrpairs,
    cowplot::plot_grid(
        hm_ipms_hot,
        gg_rnaviolin,
        NULL,
        NULL,
        ncol = 1,
        rel_heights = c(1.25, 0.75, 1, 1),
        labels = c("", "C", "D", "E")
    ),
    rel_widths = c(1, 0.65), 
    scale = 0.9, nrow = 1,
    labels = c("A", "B")
)
```

>>>>

```{r load-packages, class.source="fold-show"}
suppressPackageStartupMessages({
    library(SingleCellExperiment)
    library(ggplot2)
    library(cowplot)
    library(dplyr)
    library(forcats)
    library(jsonlite)
    library(ComplexHeatmap)
    library(colorspace)
    library(circlize)
    library(scattermore)
    library(tidyr)
    library(einprot)
})

@@

## Supplementary plots - PCA (IP-MS)

```{r}
## Low salt
sce150_pca <- einprot::doPCA(
    sce150[rowSums(!assay(sce150, 
                          metadata(sce150)$aNames$assayImputIndic)) >= 2, ],
    metadata(sce150)$aNames$assayImputed)$sce
df <- scuttle::makePerCellDF(sce150_pca, features = NULL, use.coldata = TRUE, 
                             use.dimred = TRUE) |>
    dplyr::mutate(Protocol = .capitalize(sub("_digest|_freeze", "", sub("SOP_", "", Protocol))))
pcvar150 <- attr(reducedDim(sce150_pca, "PCA_log2_LFQ.intensity"), "percentVar")
(ggpca1 <- ggplot(
    df, 
    aes(x = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".1")]], 
        y = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".2")]], 
        color = Protocol)) + 
    geom_point(size = 3, alpha = 0.5) +
    scale_color_manual(values = c(Plate = main_colors[1], 
                                  Tube = main_colors[5]), name = "") + 
    coord_fixed() + 
    labs(x = paste0("PC1 (", round(pcvar150[1], 1), "%)"), 
         y = paste0("PC2 (", round(pcvar150[2], 1), "%)"), 
         title = "150 mM NaCl") + 
    theme_cowplot() + 
    theme(legend.position = "bottom") + 
    guides(color = guide_legend(nrow = 1, byrow = TRUE)))
(ggpca2 <- ggplot(
    df |>
        dplyr::mutate(bait = ifelse(Gene_name == "atf1", "Atf1", "Other baits")) |>
        dplyr::mutate(prot = .capitalize(prot)), 
    aes(x = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".1")]], 
        y = .data[[paste0("PCA_", metadata(sce150)$aNames$assayImputed, ".2")]], 
        color = bait, shape = prot)) + 
    geom_point(size = 3, alpha = 0.5) +
    scale_color_manual(values = c(Atf1 = main_colors[3], 
                                  `Other baits` = na_color), name = "") + 
    scale_shape_manual(values = c(Plate = 16, Tube = 17), name = "") + 
    coord_fixed() + 
    labs(x = paste0("PC1 (", round(pcvar150[1], 1), "%)"), 
         y = paste0("PC2 (", round(pcvar150[2], 1), "%)"), title = "150 mM NaCl") + 
    theme_cowplot() + 
    theme(legend.position = "bottom", legend.box = "vertical", 
          legend.box.just = "left", legend.margin = margin()))

sce500_pca <- einprot::doPCA(
    sce500[rowSums(!assay(sce500, metadata(sce500)$aNames$assayImputIndic)) >= 2, ],
    metadata(sce500)$aNames$assayImputed)$sce
df <- scuttle::makePerCellDF(sce500_pca, features = NULL, use.coldata = TRUE, 
                             use.dimred = TRUE)
pcvar500 <- attr(reducedDim(sce500_pca, "PCA_log2_LFQ.intensity"), "percentVar")
(ggpca3 <- ggplot(
    df |>
        dplyr::mutate(bait = ifelse(Gene_name == "atf1", "Atf1", "Other baits")), 
    aes(x = .data[[paste0("PCA_", metadata(sce500)$aNames$assayImputed, ".1")]], 
        y = .data[[paste0("PCA_", metadata(sce500)$aNames$assayImputed, ".2")]], 
        color = bait)) + 
    geom_point(size = 3, alpha = 0.5) +
    scale_color_manual(values = c(Atf1 = main_colors[3], 
                                  `Other baits` = na_color), name = "") + 
    coord_fixed() + 
    labs(x = paste0("PC1 (", round(pcvar500[1], 1), "%)"), 
         y = paste0("PC2 (", round(pcvar500[2], 1), "%)"), 
         title = "500 mM NaCl") + 
    theme_cowplot() + 
    theme(legend.position = "bottom", legend.box.just = "left"))
```

@@

cowplot::plot_grid(
    gg_enrpairs,
    cowplot::plot_grid(
        hm_ipms_hot,
        gg_rnaviolin,
        ggpca2,
        ggpca3,
        ncol = 1,
        rel_heights = c(1.25, 0.75, 1.1, 0.9),
        labels = c("", "C", "D", "E")
    ),
    rel_widths = c(1, 0.65), 
    scale = 0.9, nrow = 1,
    labels = c("A", "B")
)
```
